---
title: "shot chart preprocessing"
output: html_document
---

```{r setup}
library(tidyverse)
library(reticulate)
library(knitr)
library(lubridate)
shot_data <- read_csv("./data/shot_chart_details.csv")
```

The dataset has over 2 million entries, so let's clear some of the bloat.

## TODO

I want to filter based on number of shots taken, but I want more recent players to have a lower requirement
```{r}
mid <- median(shot_data %>% pull(GAME_DATE))

shots <- shot_data %>% add_count(PLAYER_NAME) %>% filter(n>3500)
print(shots)
```

we got it under a million records. I think that's workable for now. Now let's fix the dates on the jawn. How about month/day/year? 

```{r}
shots <- shots %>% mutate(GAME_DATE = paste(substr(GAME_DATE, 5, 6), substr(GAME_DATE, 7,8), substr(GAME_DATE, 1,4), sep="-"))
print(shots %>% select(GAME_DATE))
```
Much Better!

```{r echo=FALSE}
shots %>% write_csv("./data/shot_chart_cleaned.csv")
```

## Some preliminary visualizations

```{r}
shots <- shots %>%
  mutate(year = year(mdy(GAME_DATE)))

shots %>% ggplot(mapping = aes(x = year, fill = SHOT_TYPE)) + geom_bar(position = "fill")

```
 We find that the shot-zone-range variable actually gives us better insights here 
```{r}
  shots %>% ggplot(mapping = aes(x = year, fill = SHOT_ZONE_RANGE)) + geom_bar(position = "fill")

  shots %>% filter(PLAYER_NAME == "Stephen Curry") %>% ggplot(mapping = aes(x = PLAYER_NAME, y=SHOT_DISTANCE)) + geom_violin(trim=FALSE)
```



```{r}

```


